\section*{Declarations}

\subsection*{Funding}

This research received no external research funding.

\subsection*{Ethics approval and consent to participate}

This study used only publicly available databases and did not involve human participants, human tissue, or animal experiments; no ethics approval or informed consent was required.

\subsection*{Acknowledgements}

The authors acknowledge the use of AI assistant tools for code-development support, debugging, language editing, and manuscript-organization assistance, as disclosed in the Methods section. All analyses, results, and interpretations were verified by the authors.

\subsection*{Author contributions}

A.B. conceived and designed the study, developed the analytical framework, curated the data, conducted the computational and statistical analyses, generated the figures, interpreted the results, and drafted the initial manuscript. S.M. contributed to data verification, methodological discussion, refinement of result presentation, and critical revision of the manuscript. V.T.M. supervised the study, provided scientific and methodological guidance, contributed to interpretation of the findings, and critically revised the manuscript. All authors read and approved the final manuscript.

\subsection*{Competing interests}

The authors declare no competing interests.

\subsection*{Additional information}

\noindent\textbf{Correspondence} and requests for materials should be addressed to V.T.M.

\noindent\textbf{Email:} \href{mailto:vijayakm2@srmist.edu.in}{vijayakm2@srmist.edu.in}.

\noindent\textbf{ORCID iDs:} Antony Bevan, \href{https://orcid.org/0009-0002-3676-2042}{0009-0002-3676-2042}; Vijayakumar Thangavel Mahalingam, \href{https://orcid.org/0000-0002-7749-3224}{0000-0002-7749-3224}.
